Claret: Using Data Types for Highly Concurrent Distributed Transactions

### 2015-03-14 rmd/paper.Rmd
adjust figure 4 (move legend to bottom)

```{r throughput, include=F, fig.height=2.1}
d <- data(db("
    select * from tapir where 
    generator_time is not null and total_time is not null
    and name like 'claret-v0.14%'
  ",
    factors=c('nshards', 'nclients'),
    numeric=c('total_time', 'txn_count')
))
d.u <- subset(d, nshards == 4 & initusers == 4096 & nclients != 96 & nclients != 128
                & grepl('geom_repost|read_heavy', mix))
ggplot(d.u, aes(x=nclients, y=throughput/1000, 
        group=cc, fill=cc, color=cc, linetype=cc))+
    stat_summary(fun.y=mean, geom="line", size=0.4)+
    xlab('Concurrent clients')+ylab('Throughput (k trans. / sec)')+
    expand_limits(y=0)+
    facet_wrap(~workload)+
    theme_mine+
    theme(legend.position='right', legend.direction='vertical', legend.title.align=0)+
    cc_scales(title='Concurrency\ncontrol:')
```
\begin{figure}[t]
\centering
\includegraphics{figure/throughput-1.pdf}
\caption{Throughput of social network workload (Retwis) with 4000 users.
Leveraging commutativity prevents performance from falling over even
when posts spread virally (repost-heavy).\label{tput}}
\end{figure}

>>>>

```{r throughput, include=F, fig.width=2.5, fig.height=2.8}
d <- data(db("
    select * from tapir where 
    generator_time is not null and total_time is not null
    and name like 'claret-v0.14%'
  ",
    factors=c('nshards', 'nclients'),
    numeric=c('total_time', 'txn_count')
))
d.u <- subset(d, nshards == 4 & initusers == 4096 & nclients != 96 & nclients != 128
                & grepl('geom_repost|read_heavy', mix))
ggplot(d.u, aes(x=nclients, y=throughput/1000, 
        group=cc, fill=cc, color=cc, linetype=cc))+
    stat_summary(fun.y=mean, geom="line", size=0.4)+
    xlab('Concurrent clients')+ylab('Throughput (k trans. / sec)')+
    expand_limits(y=0)+
    facet_wrap(~workload)+
    theme_mine+
    theme(legend.position=c(0.5,-0.25), plot.margin=unit(c(.5,.5,8,.5),'mm'), legend.direction='horizontal', legend.title.align=1)+
    cc_scales(title='Concurrency\ncontrol:')
```
\begin{figure}[t]
\centering
\includegraphics{figure/throughput-1.pdf}
\caption{Throughput of social network workload (Retwis) with 4000 users.
Leveraging commutativity prevents performance from falling over even
when posts spread virally (repost-heavy).\label{tput}}
\end{figure}
